An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-04-22 CMPSpaper_writing/CMPSpaper_writing.Rmd
taking include.graphics out for sigplot1 and sigplot2 and replacing by code

```{r, eval=FALSE}
library(CMPS)
data(bullets)
```

@@

```{r, eval=FALSE}
sigs1 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
sigs2 <- bullets$sigs[bullets$bulletland == "1-4"][[1]]

@@

```{r eval=FALSE}
dframe %>% 
  ggplot(aes(x = land1, y = land2, fill = CMPS.score)) +
    geom_tile() +
    scale_fill_gradient2(low="darkgrey", high = "darkorange", mid=6) +
    geom_text(aes(label=CMPS.score))
```

@@

We also implemented graphing tools for visualizing results of the CMPS algorithm. The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works. Let's continue with the example above and take its results.

```{r, eval=FALSE}
sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
```

@@

\hh{XXX Could we move the code into the corresponding figure and show the relevant pieces side by side? I'm thinking of examples similar to p.38 in https://journal.r-project.org/archive/2017/RJ-2017-023/RJ-2017-023.pdf}
```{r, eval=FALSE}
sig.plot$segment_shift_plot
```

```{r, echo=FALSE, out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison signature; each red line segment shows one comgruent matching profile segment. "}
knitr::include_graphics("img/sigplot1.png", dpi = 100)
```

@@

```{r, eval=FALSE}
sig.plot$signature_shift_plot
```

```{r, echo=FALSE, out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background? XXX} The dark grey line shows the comparison signature; the red line shows the reference signature. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position. "}
knitr::include_graphics("img/sigplot2.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments. "}
knitr::include_graphics("img/segplot1.png", dpi = 100)
```

>>>>

```{r, eval=TRUE}
library(CMPS)
data(bullets)
```

@@

```{r, eval=TRUE}
sigs1 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
sigs2 <- bullets$sigs[bullets$bulletland == "1-4"][[1]]

@@

```{r eval=FALSE}
dframe %>% 
  ggplot(aes(x = land1, y = land2, fill = CMPS.score)) +
    geom_tile() +
    scale_fill_gradient2(low="darkgrey", high = "darkorange", mid=6) +
    geom_text(aes(label=CMPS.score))

```

@@

We also implemented graphing tools for visualizing results of the CMPS algorithm. The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works. \autoref{fig:sigplot} continues with the example above and take its results.

@@

\hh{XXX Could we move the code into the corresponding figure and show the relevant pieces side by side? I'm thinking of examples similar to p.38 in https://journal.r-project.org/archive/2017/RJ-2017-023/RJ-2017-023.pdf}

<!--
```{r, eval=FALSE}
sig.plot$segment_shift_plot
```
-->
```{r sigplot, echo=TRUE,  out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison signature; each red line segment shows one comgruent matching profile segment. "}
sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
sig.plot$segment_shift_plot
#knitr::include_graphics("img/sigplot1.png", dpi = 100)
```

@@

<!--
```{r, eval=FALSE}
sig.plot$signature_shift_plot
```
-->

```{r, echo=TRUE, eval=TRUE,  out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background? XXX} The dark grey line shows the comparison signature; the red line shows the reference signature. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position. "}
sig.plot$signature_shift_plot
#knitr::include_graphics("img/sigplot2.png", dpi = 100)
```

@@

```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments. "}
knitr::include_graphics("img/segplot1.png", dpi = 100)
```
